\documentclass[lighthipster]{styles}
% available options are: darkhipster, lighthipster, pastel, allblack, grey, verylight, withoutsidebar

\usepackage[utf8]{inputenc}
\usepackage[default]{raleway}
\usepackage[margin=0.65cm, a4paper]{geometry}

\usepackage{multicol}

\usepackage{hyperref}
\hypersetup{pdfborder = 0 0 0}

\usepackage{enumitem}

\renewcommand{\Huge}{\fontsize{30}{15}\selectfont}
\renewcommand{\huge}{\fontsize{16}{15}\selectfont}
\renewcommand{\Large}{\fontsize{12}{12}\selectfont}
\renewcommand{\large}{\fontsize{11}{10}\selectfont}
\renewcommand{\normalsize}{\fontsize{10.2}{12}\selectfont}


%------------------------------------------------------------------ Variablen

\newlength{\rightcolwidth}
\newlength{\leftcolwidth}
\setlength{\leftcolwidth}{0.1\textwidth}
\setlength{\rightcolwidth}{0.9\textwidth}

%------------------------------------------------------------------
\pagestyle{empty}
\begin{document}

\setlist[itemize]{leftmargin=*, itemsep=0.2em}


\thispagestyle{empty}
%-------------------------------------------------------------

\section*{Start}

% \tikz[remember picture,overlay] {%
% \node[rectangle, fill=#1, anchor=north, minimum width=\paperwidth, minimum height=3.5cm](header) at (current page.north){};%
% \node[draw=none, align=left](name) at (header) {%
% {\Huge \color{#5} #2 \textbf{#3} }%
% };%
% \node[draw=none, below](description) at (name.south) {\color{white}#4};% 
% }\vspace{-0.7cm}%

\simpleheader
{Ryan Mah}
{+1 (403) 992-8880}
{contact@ryan-mah.com}
{\href{https://github.com/RyanJMah}{github.com/RyanJMah}}
{\href{https://ryan-mah.com}{ryan-mah.com}}

%------------------------------------------------

% this has to be here so the paracols starts..
\subsection*{}
\vspace{1.7cm}

\setlength{\columnsep}{1cm}
\columnratio{0.285}
\begin{paracol}{2}
% \hbadness5000
%\backgroundcolor{c[1]}[rgb]{1,1,0.8} % cream yellow for column-1 %\backgroundcolor{g}[rgb]{0.8,1,1} % \backgroundcolor{l}[rgb]{0,0,0.7} % dark blue for left margin

% \paracolbackgroundoptions

% 0.9,0.9,0.9 -- 0.8,0.8,0.8


% \renewcommand{\normalsize}{\fontsize{12}{10}\selectfont}


% \footnotesize
{
\flushleft

\setlength\columnsep{0.4cm} % This is the default columnsep for all pages

% \bg{ryanHeadingBg}{white}{\textbf{Summary}}\\[0.5em]
\section*{Summary}
\vspace{0.1cm}

\begin{itemize}
    \item 5+ years of proven experience in C and Python
    \item 4+ years of embedded programming experience (bare-metal and RTOS)
    \item 4+ years of HW and PCB design experience
\end{itemize}

\vspace{0.05cm}

\section*{Education}
\subsection*{University of Waterloo}
\subsubsection*{BASC. Electrical Engineering} \vspace{-0.075cm}
\subsubsection*{\color{ryanGrey}2019 - 2024}
\begin{itemize}
    \item Cummulative Average: 87\%
\end{itemize}

\vspace{0.05cm}

\section*{\textbf{Skills}}
\subsection*{Languages}
\vspace{-0.4cm}
\begin{multicols}{2}
    \begin{itemize}
        \item C
        \item C++
        \item Assembly (ARM, RISC-V)
        \item Make
        \item Python
        \item Bash
        \item Verilog
    \end{itemize}
\end{multicols}

\subsection*{Technologies}
\vspace{-0.4cm}
\begin{multicols}{2}
    \begin{itemize}
        \item ARM
        \item RISC-V
        \item STM32
        \item SPI
        \item I2C
        \item UART
        \item CAN
        \item Ethernet
        \item USB
        \item LoRaWAN
        \item gcc
        \item clang
        \item gdb
        \item FreeRTOS
        \item nrf5 SDK
        \item Linux
        \item TCP
        \item UDP
        \item MQTT
    \end{itemize}
\end{multicols}

\subsection*{Tools}
\vspace{-0.4cm}
\begin{multicols}{2}
    \begin{itemize}
        \item git
        \item Vitis
        \item Altium
        \item LTSpice
    \end{itemize}
\end{multicols}

\subsection*{Lab}
\vspace{-0.4cm}
\begin{multicols}{2}[]
    \begin{itemize}
        \item Spectrum Analyzer
        \item Soldering
        \item Network Analyzer
        \item Oscilloscope
    \end{itemize}
\end{multicols}

}
%-----------------------------------------------------------
\switchcolumn

\section*{Experience}

\experienceHeading{Apple}
{Firmware Intern (Silicon Engineering Group)}
{Sep. 2023 - Dec. 2023}
\begin{itemize}
    \item Developed and tested low-level FW for Apple's SoCs
    \item Implemented and enhanced cryptography FW ROM, used in many different SoCs
\end{itemize}

\experienceHeading{Level Home}
{Firmware Developer}
{Jan. 2023 - Apr. 2023}
\begin{itemize}
    \item Implemented the HomeKit FW update service, allowing users to update lock
          firmware over BLE with the Apple Home iPhone app
    \item Patched firmware to decrease frequency of false positive NFC wakes
          causing excess battery drain, decreasing percentage of defective
          units from 1.5\% to 0.5\%
    \item Root-caused and fixed critical issues, including flash filesystem
          corruption, battery drain in cold temperatures, and false NFC wakes
\end{itemize}

\experienceHeading{Siemens (Enlighted)}
{Firmware Engineer, IoT Platform \& MACs}
{May 2022 - Aug. 2022}
\begin{itemize}
    \item Worked on an Agile team to develop and support applications for Enlighted's
          IoT lighting platform, including FreeRTOS sensors and embedded Linux devices
    \item Reworked packet parsing library to increase flexibility and improved speed by $\sim$40\%
\end{itemize}

\experienceHeading{TEKTELIC Communications}
{Systems Engineering}
{May 2020 - Aug. 2020 $\;\cdots\;$ Jan. 2021 - Apr. 2021}
\begin{itemize}
    \item Implemented scripts for the complete automation of conducted emissions
          compliance tests for 800MHz (ETSI) and 900MHz (FCC) bands
\end{itemize}

\experienceHeading{Waterloop Hyperloop Design Team}
{Electrical \& Firmware Lead}
{Sep. 2019 - Jan. 2023}
\begin{itemize}
    \item Led the hardware and firmware development of all embedded devices on the hyperloop
          pod - including BMS, motor controller, central computer, and more
    \item Main developer for BMS software, including pack voltage \& current sensing,
          state-of-charge monitoring, cell voltage monitoring over isoSPI, state machine, CAN, etc.
\end{itemize}

\section*{Projects}

\experienceHeading{GuidingLite}
{Final-Year Capstone Project (University of Waterloo)}
{May 2023 - Mar. 2024}
\begin{itemize}
    \item Led the development of an ultra-wideband (UWB) 2D indoor navigation system,
          with accessibility features for the visually impaired
    \item UWB “anchors” interface with the Apple U1 chip in a user's iPhone to enable
          accurate, soft real-time indoor positioning and pathfinding
    \item Designed custom anchor PCBs in Altium, complete with PoE, BLE, and a UWB SoC
    \item Wrote the anchor FW in C, including two-way ranging, telemetry, and a TCP
          bootloader for on-the-fly debugging
    \item Implemented weighted-least-squares multilateration for robust 3D localization 
    \item Engineered a 2D pathfinding solution by overlaying a navigation mesh onto a
          floorplan for efficient navigation
\end{itemize}



\end{paracol}

\end{document}
